Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2019-05-05 LatexNotes/Notes.tex
NM

>>>>

\subsection{The optimizer of the Hamiltonian is a traveling wave solution}
For the acceptance-rejection algorithm presented below, it will be important to find the maximal value of the Hamiltonian subject to the constraints of fixed energy $E = E_0$ and zero momentum $M = 0$. For simplicity, consider the KdV equation
\begin{equation}
u_t + u u_x + \mu u_{xxx} = 0
\end{equation}
with corresponding Hamiltonian
\begin{equation}
H = \frac{1}{6} \intt u^3 dx - \frac{\mu}{2} \intt u_x^2 dx
\end{equation}

Consider the functional
\begin{equation}
F[u] = H[u] + \lambda_1 (E-E_0) + \lambda_2 (M-0)
\end{equation}
where $\lambda_1$ and $\lambda_2$ are Lagrangian multipliers. Taking the variational derivative gives
\begin{equation}
\frac{\delta F}{\delta u} = \frac{1}{2} u^2 + \mu u_{xx} + \lambda_1 u + \lambda_2 = 0
\end{equation}
which is a second-order nonlinear ODE for the optimizer $u = U(x)$. Note that this is identical to the condition for a traveling wave solution!!!
